Spatial variation of coronal Fourier power spectra

### 2016-02-17 tex/paper2/paper2.tex
updating all the modifieds so as not lose anything

@@

It is shown that in almost all locations the \Fps\ are well be described by
a \PL\ at lower frequencies that tails to flat spectrum at higher
frequencies, plus a Gaussian-shaped contribution that varies depending
on the region studied.

@@

Other types of oscillatory behavior have been observed.
\cite{2005ApJ...620.1101M} demonstrate the presence of oscillatory
power with periods in the range of 40-80 seconds using high-cadence
H$\alpha$ blue wing observations of a Geostationary Operational
Environmental Satellite (GOES) C9.6-class solar flare obtained at Big
Bear Solar Observatory using the Rapid Dual Imager
\citep{2000SoPh..193..259P, 2007A&A...473..943J}. The measured
properties of these oscillations are consistent with the existence of
flare-induced acoustic waves within the overlying loops.  In addition,
\cite{2013ApJ...772...54A} show that the oscillatory power in the
lower solar atmosphere of active regions increases in response to
flare events at distant solar locations.

The relative scarcity of observations of coronal oscillations has
prompted efforts to create automated oscillation detection algorithms.
The need for an automated oscillation detection algorithm has been
exacerbated by the large and rapidly growing amount of {\BF Solar
  Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P})
  Atmospheric Imaging Assembly (AIA, \citealp{2012SoPh..275...17L})}
data.  There have been several attempts at designing such algorithms.
\cite{2004SoPh..223....1D} describe the design of an automated
oscillation-detection algorithm based on wavelet analysis. The
algorithm finds significant wave packets ranging from single to
multiple wave cycles in duration, by a wavelet power/confidence level
comparison against the null hypothesis that a given time series is
Gaussian-distributed noise.  Pixels with significant oscillatory
content are grouped manually.  \cite{2007SoPh..241..397N} take a
similar approach, using a thresholded fast Fourier transform to find
locations in TRACE data that may support an oscillatory signal. The
threshold level is defined as three to four times the average fast
Fourier transform (FFT) power; if the maximum FFT power is above this
level then the frequency at which that power occurs is assumed to be
real. \cite{2010SoPh..264..403I} assume that an oscillatory signal is
present in each location in the datacube and then use a Bayesian-based
treatment to calculate the probability that the frequency has a
particular value.  This algorithm relies on subtracting a background
trend from the time-series being tested, and assumes that the noise is
Gaussian distributed.

The above algorithms precipitate detections based on the strength of
the signal of an oscillation on a pixel by pixel basis, and then group
these pixels together using some set of criteria.  The automated
detection algorithm of \cite{2008SoPh..248..395S} begins by
identifying candidate oscillatory regions as those whose time-series
of emission show a high variance \citep{2003SoPh..213..103G} (under
the implicit assumption that the time-series has an approximately
constant mean value).  Detections are based on wavelet filtering of
these regions in all three dimensions of the data cube simultaneously,
with the implicit assumption that the noise is Gaussian-distributed.
{\BF The algorithm of \cite{2008SoPh..252..321M} differs from the
  previous algorithms: it begins by Fourier transforming the entire
  data cube, and calculating the coherence of neighboring pixels in
  narrow frequency bands, and filtering the results. The null
  hypothesis here is that pairs of time series that have low coherence
  can be rejected as being part of an oscillatory group.  This method
  uses a symmetric filter to estimate the coherence, in that
  oscillatory power from either side of the central search frequency
  contributes the same weight to the final result.  There is an
  implicit assumption here that the power on either side of the
  central search frequency is approximately the same.  In this
  algorithm, the spatial extent of the coherence of the oscillatory
  signal is the key identifier of a wave process.}

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and
(approximately) Gaussian-distributed noise which must be taken in to
account in order to test for the presence of an oscillatiory signal
{\BF \citep{2004SoPh..223....1D, 2007SoPh..241..397N,
    2008SoPh..248..395S, 2010SoPh..264..403I, 2013SoPh..286..405C}.}
{\BF However, two recent papers cast doubt on this assumption.
  \cite{2014AA...563A...8A} integrate emission over small portions of
  active regions and the quiet Sun as observed in the 195\AA\ passband
  images from EIT and show that the resulting time-series has an
  approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
  \citet{gupta2014} showed \PL\ \PA\ in the intensity at six single
  points in AIA 171\AA\ coronal plumes extending over the frequency range
  $0.3\rightarrow 4.0$ mHz.}

The aim of this paper is to determine how the observed coronal Fourier
power spectra varies as a function of space and AIA channel.

 The nature
of coronal emission has implications for coronal seismology, and may
be indicative of the nature of the fundamental energy deposition that
keeps the corona hot.

@@

\section{Observations}\label{sec:obs}
The region studied is the same as that used in the previous
\cite{ireland2015} study.  The selected area covers a single
$\beta\gamma$ active region, NOAA AR 11575.  As was noted in
\cite{ireland2015} , this area is quiescent in that there were no
X-ray flares or other large-scale disturbances (for example, filament
eruptions or rearrangments of long bright coronal loops) over the
spatial extent of the cutout within the time range.  Since the area of
the cutout also contains a sunspot, previous observations
\citep{2002A&A...387L..13D} suggest that it is highly likely that
three-minute oscillations will be present in AIA coronal channels.

{\BF AIA} observes images of the Sun in multiple channels
simultaneously and continuously, at high cadence (12 seconds) and at
high spatial resolution (0.6 arcseconds per pixel).  {\BF AIA} data
was acquired using the Lockheed Martin Solar Astrophysics cutout
service at {\it http://lmsal.com/get\_aia\_data/}.  Six hours of image
data in the time range 2012-09-23 00:00 - 06:00 UT, at the full 12
second cadence, in EUV wavebands 171\AA, 193\AA, 211\AA, 335\AA,
131\AA\ and 94\AA\ are used.  The data in each AIA channel are
co-aligned to remove solar rotation using the process as described in
Appendix \ref{sec:app:data}.  The result are a set of datacubes that
retain show the same portion of the Sun for the duration of the data.

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{{\BF The proportion of the number of pixels in each image
    that have a given Fourier power at some sample Fourier
    frequencies.  The left hand column gives results for AIA 171\AA,
    and the right hand column, AIA 193\AA.  Regions are indicated in
    each plot title.}}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} shows the probability distribution of the
Fourier power of the pixels in each region at five selected
frequencies, for all the pixels in each region.  These distributions
are centrally peaked, show a slightly heavier tail towards lower
Fourier powers (negative skew), are slightly broader when compared to
a Gaussian distribution, and are all unimodal.  These observations
guide the choice of how to average the \PS\ over each of the selected
region.  The nature of these distributions suggest that the arithmetic
mean of the Fourier power is biased by the very largest powers.
Therefore, the mean value of the logarithm of the Fourier power is a
better description of the range of values in the data (this is
equivalent to the geometric mean of the Fourier power).  The \PA\ used
below are calculated from the mean value of the logarithm of the
Fourier power.

\begin{figure}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\begin{singlespace}
 \caption{Geometric mean of the \protect\Fpa\ (black
    solid line) in each of the four regions studied in AIA
    171\AA\ (left column) and AIA 193\AA\ (right column).  Also shown
    are the posterior mean fits for model $M_{1}$ and $M_{2}$ (blue
    and red lines respectively; see Section \ref{sec:anal} and
    Appendix \ref{sec:app:ind} for more detail).  The AIC describing
    the preference for model over the other is also indicated in each
    plot.  The reduced $chi^{2}_{r}$ statistic for Model 1 and Model 2
    are given. The two components to Model 2, $P_{1}(\nu)$ and
    $G(\nu)$ are also shown in green; the location of the maximum of
    the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the green dotted
    line.  Model fit parameter values and their 68\% credible
    intervals are quoted in Table \ref{tab:parameters}.}
\end{singlespace}
\label{fig:fit171193}

\end{figure}

The (geometric) \mFpa\ are shown in Figure \ref{fig:fit171193} for
each of the physical regions considered.  It is clear that, in
general, the \mFpa\ exhibit power-law like characteristics.  The
results for the quiet Sun, loop footpoints and sunspot regions suggest
a \PL\ \PS.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A_{p}\nu^{-n} + C,
\end{equation}
where $\nu$ is the frequency, $A>0$ is a proportionality constant and
$n>0$ is the \PL\ index.  The quantity $C>0$ models the high-frequency
/ low power end of the spectrum where the detection properties of the
detector apparatus are assumed to dominate the observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that {\BF TRACE}
171\AA\ time-series of bright upper transition region emission above
active region plage (also known as moss) is a source of wavelet
power. Periods of significant wavelet power are found in the range 200
to 600 seconds, and typically persist for 4–7 cycles.  Later work by
\cite{2005ApJ...624L..61D} suggested that spicule flux tubes tilted
with respect to the solar surface provide a mechanism by which
oscillatory power from lower in the atmosphere may be channeled to
upper portions of the atmosphere.  This suggests that a second model
$M_{2}$ for the \Fps\ in regions should be considered.  The second
model $M_{2}$ has two contributions to the overall \Fps; a background
power-law of the form of $P_{1}$, and a contribution that is more
localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = A_{G}\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}).  {\BF Model fitting and parameter estimation are
  implemented using a Bayesian probability based approach.}  This
approach was chosen for its flexibility and consistent error
estimation properties \citep{2013ApJ...769...89I}.  The details of the
model fitting process are described in Appendix \ref{sec:app:ind}.
The position of $G(\nu)$ is restricted by permitting $\beta$ to vary
in the range $0.1-10$ mHz only.  This restriction, which is imposed in
the fitting process (see Appendix \ref{sec:app:ind}), arises from the
observations of significant wavelet power in the period range 200 -
600 seconds as found by \cite{2003ApJ...595L..63D}.  {\BF After this
  fitting process is complete, the models are compared to decide which
  model best describes the data.  The details of the model comparison
  process are described in the following section.}

\subsection{Results}\label{ssec:results}
Figure \ref{fig:fit171193} show the fit results of each model to the
data.  For details on the fitting procedure, see Appendix
\ref{sec:app:ind}.
{\BF The two models are assessed for how well they describe the data in two
different ways. Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that Model 2 loses less information compared to Model 1,
leading to a preference for Model 2 over Model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
{\BF The AIC reveals which (out of a set of models) is preferred.  It
  does not give an assessment of the goodness-of-fit of each model.
  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
  $\chi^{2}_{r}=\sum_{j=1}^{N}\left[(P_{i}(\nu_{j})-D_{j})/\sigma_{j}^{2}\right]/(N-k-1)$,
  where $N=899$ is the number of frequencies, $P_{i}(\nu_{j})$ is the
  model power $P_{i}$ at frequency $\nu_{j}$, $D_{j}$ is the \mFpa\ at
  $\nu_{j}$, and $\sigma_{j}$ is the estimated standard deviation of
  the data $D_{j}$ (see Appendix \ref{sec:app:ind} for more details of
  the estimation of $\sigma_{j}$).  The value of $\chi^{2}_{r}$ is
  calculated for both models.  Note that the \mFpa\ are only
  approximately normally distributed, and so caution must be used in
  interpreting $\chi^{2}_{r}$. Since $N>>k$, $\chi^{2}_{r}$ is
  understood as a measure of the average scaled variance of the model
  fit to the data. Within the approximations of the analysis, the
  $\chi^{2}_{r}$ measures show that reasonable fits are obtained for
  Model $M_{2}$ in all cases, excepting the loop footpoints.  The
  relatively low value of $\chi^{2}_{r}$ for these locations indicate
  that probably the size of $\sigma_{i}$ are over-estimated.}

@@

\begin{deluxetable}{cccccccccc}
\tabletypesize{\scriptsize} \tablecolumns{5} \tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
  model \protect$M_{2}$.  {\BF Uncertainties with an absolute value
    less than $0.005$ are quoted as $0.00$.} {\BF Uncertainties with
    an absolute value between 0.005 and 0.01 are rounded up to have an
    absolute value of 0.01} \label{tab:parameters}} \tablehead{
  \colhead{Region} & \colhead{Waveband} &
  \multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal
    $G(\nu)$} & \multicolumn{2}{c}{ratio
    $P_{1}(\nu)/G(\nu)$}\\ \colhead{} & \colhead{} &
  \colhead{$\log_{10}A$} & \colhead{$n$} & \colhead{$\log_{10}C$} &
  \colhead{$\log_{10}\alpha$} & \colhead{$\beta$ (mHz)} &
  \colhead{$\delta$\tablenotemark{1}} & \colhead{$\max$} &
  \colhead{$\arg\max$ (mHz)} \\ } \startdata loop footpoints & 171\AA
& $0.55^{+0.02}_{-0.02}$ & $2.29^{+0.02}_{-0.02}$ &
$-4.26^{+0.00}_{-0.00}$ & $-2.30^{+0.09}_{-0.08}$ &
$0.69^{+0.09}_{-0.08}$ & $0.32^{+0.01}_{-0.01}$ & 1.45 & 2.22 \\ &
193\AA & $0.06^{+0.03}_{-0.02}$ & $2.28^{+0.04}_{-0.05}$ &
$-4.40^{+0.00}_{-0.00}$ & $-2.18^{+0.16}_{-0.22}$ &
$0.28^{+0.11}_{-0.06}$ & $0.43^{+0.03}_{-0.04}$ & 1.58 & 1.90 \\ & & &
& & & & & & \\

moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & 5.19 & 2.45\\
                & 193\AA  & $0.39^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.49^{+0.00}_{-0.00}$  & $-2.00^{+0.02}_{-0.02}$  & $1.24^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & 4.72 & 2.68 \\
                & & & & & & &   & & \\

quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & 0.20 & 4.63 \\
                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.52^{+0.00}_{-0.00}$  & $-4.75^{+0.05}_{-0.05}$  & $4.68^{+0.18}_{-0.17}$  & $0.11^{+0.01}_{-0.01}$    & 0.08 & 4.72 \\
                & & & & & & &   & & \\

sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.01}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.80^{+0.02}_{-0.02}$  & $1.83^{+0.05}_{-0.05}$  & $0.32^{+0.00}_{-0.00}$    & 2.07 & 3.56 \\
                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.14^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.04^{+0.03}_{-0.03}$  & $1.59^{+0.07}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & 1.55 & 3.15 \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\tablenotetext{1}{Values are quoted in decades of frequency}
\end{deluxetable}

@@

\subsection{Effect of background \PS\ assumptions on the
  detection of oscillatory power}
\label{ssec:corseis}

Section \ref{sec:anal} demonstrates the presence of an approximate
\PL\ \PS\ signal in two of the most commonly used wavebands for
coronal seismology, SDO/AIA 171\AA\ and 193\AA.  The observed spectra
generally show a \PL-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non \PL\ \PS\ source over a relatively limited range of frequencies.
The frequencies at which the lognormal contribution is larger than the
underlying power-law distribution could be used to define an average
frequency range within which the majority contribution to the overall
Fourier power is not associated with the underlying power-law
distribution.  However, the \Fps\ in this range would still have to be
analyzed using both the power-law and lognormal contributions to the
overall power, and better estimates to the power-law parameters will
be obtained if the full frequency range of the observations are used.

The presence of a non \PL\ contribution to the \Fps\ does not change
the fact that the background emission is essentially power-law like.
For the frequencies that have been of interest in coronal seismology,
the background \PS\ is therefore scale free on average.  If there is
no time-scale that can be used to remove a background trend, then the
time-series has to be analyzed without this processing step.  However,
a lack of awareness of the background \PL\ \PS\ nature of the emission
will cause significant problems in attempting to analyze for the
presence of narrow frequency band oscillations, as the following
example demonstrates.

\begin{figure}
\epsscale{1.00}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or
  \PL\ \PS\ background on the detection of an oscillatory signal for
  simulated time-series.  Plot (a) shows the simulated time-series,
  generated from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming the null hypothesis that the
  time-series is purely noise, and that the noise has the same average
  power at all wavelet scales.  Plot (c) shows the global wavelet
  \protect\PS\ for this wavelet transform.  Plots (d) and (e) are the
  same as plots (b) and (c) with the null hypothesis that the
  time-series is purely noise, modeled using an auto-regressive AR(1)
  model.  Such time series assume that the current value in a
  time-series depends on its previous value plus some
  Gaussian-distributed noise (\citealp*{chatfieldtimeseries}.)  This
  time-series model gives rise to a \protect\PL\ \protect\PS\ of the
  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
  oscillation, and $n$ is its \PL\ index.  The code used in this
  analysis is an implementation of that described by
  \citet{1998BAMS...79...61T}.}
\label{fig:comparison}
\end{figure}

Figure \ref{fig:comparison} illustrates how a time series generated
from a random sample from a \PL\ \PS\ can be mistakenly thought to
contain a narrow-band oscillatory signal.  The time series in Figure
\ref{fig:comparison}(a) {\BF is a realization of a random process with
  a \PS\ of the form $P(f)\approx f^{-1.77}$ with no explicit
  oscillatory content, using the construction procedure detailed in
  \cite{2010MNRAS.402..307V}.  A different realization of the same
  process with the same \PS\ would almost certainly generate a
  different looking time-series, but since there is more power in
  lower frequencies, lower frequency components are more likely to be
  visible to the eye compared to higher frequency components.}  {\BF
  Figure \ref{fig:comparison}(b) shows that if the null hypothesis is
  that the time-series is purely noise, and that the noise has the
  same average power at all wavelet scales (for example, if the
  time-series were pure Gaussian noise), then the 95\% confidence
  level leads to the positive detection of significant oscillatory
  power in this time series.}  {\BF The detection claim changes if a
  different null hypothesis is used. Figure \ref{fig:comparison}(d) is
  the same as Figure \ref{fig:comparison}(b) except with the null
  hypothesis that the time-series gives rise to a \PL\ \PS\ of the
  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
  oscillation, and $n$ is its \PL\ index}\footnote{{\BF The model
    used to generate a \PL\ \PS\ is an auto-regressive AR(1) model.
    Such time-series assume that the current value in a time-series
    depends on its previous value plus some Gaussian-distributed noise
    \citep{chatfieldtimeseries}.  The null hypothesis that generates
    the \PL\ \PS\ is not important in order to illustrate its effect
    on the detection claim.}}.  This null hypothesis assumption, with
the same confidence level, significantly reduces the area in the
wavelet transform for which a detection may be claimed.  Even with
this significantly different background assumption, there is still a
significant amount of wavelet power above the 95\% confidence level.
However, since the data is simulated without an explicit oscillatory
component, the high wavelet power must have arisen by chance.  The
simulated data, along with the results of Section \ref{sec:anal},
suggest that when examining the wavelet transforms of time-series for
wave packets, a background \PL\ \PS\ should be assumed, along with
higher confidence levels (99\% or higher), in order to minimize the
effects of mistakenly identifying random variations in the background
\PS\ as evidence for an oscillatory signal.  {\BF Since there is a
  \PL\ \PS\ in time-series of coronal emission, evidence for the
  existence of a process that generates narrow-band oscillatory power
  has to {\BF be} measured by its power over and above that expected by the
  \PL\ \PS.}

However, even this approach to identifying oscillatory power is not
quite complete, as it simply rejects the null hypothesis that the
\PS\ can be adequately explained by a \PL\ \PS.  Model comparison
techniques similar to that described in Section \ref{sec:anal} are
required to prefer a model with oscillatory content over one
without. The difficulty in finding narrow-band features in Fourier
power spectra against a background \PL\ \PS\ has been recognized by
\cite{2010MNRAS.402..307V} in the study of XMM-Newton observations of
highly variable Seyfert 1 galaxies.  \cite{2010MNRAS.402..307V}
presents a model fitting and comparison technique that is directly
applicable to the search for oscillatory power in coronal time-series.

\subsection{Implications for coronal seismology and automated
  oscillation detection algorithms}\label{sec:oscdetect}

The discussion of Section \ref{ssec:corseis} shows that \PL\ power
spectra have a powerful effect on the claims of a detection of
narrow-frequency band oscillations in single time-series.  When
looking at extended regions of coronal imaging data, evidence for the
presence of a propagating wave in the corona is strengthened if it can
be shown that narrow frequency-band oscillations occur significantly
above the background signal in several neighboring pixels.  Spatial
extent is the key feature to claim of a detected wave.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

>>>>

\newcommand{\allaiaeuv}{171\AA, 193\AA, 211\AA, 335\AA, 94\AA\ and 131\AA}

@@

It is shown that in almost all locations the \Fps\ are well be described by
a \PL\ at lower frequencies that tails to flat spectrum at higher
frequencies, plus a Gaussian-shaped contribution that varies depending
on the region studied.  The spatial distribution of the power law
index is described as a function of AIA EUV channel.

@@

\cite{ireland2015} analyzed power spectra summed over physically
different extended regions.  It was noted that some regions, when
observed in two different AIA channels result in different power-law
power indices, while other regions have approximately similar
power-law spectral indices.  For example, loop footpoint locations had
very similar spectral index of approximately 2.28, whereas AIA 171\AA\
and 193\AA\ had spectral indices of 1.76 and 2.05 respectively.  It is
therefore clear that different regions exhibit different evolutionary
behavior.  This paper extends that work by fitting models of power
spectra arising from time-series in all six EUV channels (\allaiaeuv).
This will result in more detailed infomation on the spatial
distribution of Fourier power in the AIA EUV channels.

@@

\section{Observations}\label{sec:obs}
The region studied is the same as that used in the previous
\cite{ireland2015} study.  The selected area covers a single
$\beta\gamma$ active region, NOAA AR 11575.  As was noted in
\cite{ireland2015} , this area is quiescent in that there were no
X-ray flares or other large-scale disturbances (for example, filament
eruptions or rearrangments of long bright coronal loops) over the
spatial extent of the cutout within the time range.
\cite{ireland2015} note the power spectra

{\BF AIA} observes images of the Sun in multiple channels
simultaneously and continuously, at high cadence (12 seconds) and at
high spatial resolution (0.6 arcseconds per pixel).  {\BF AIA} data
was acquired using the Lockheed Martin Solar Astrophysics cutout
service at {\it http://lmsal.com/get\_aia\_data/}.  Six hours of image
data in the time range 2012-09-23 00:00 - 06:00 UT, at the full 12
second cadence, in EUV wavebands \allaiaeuv\ are used.  The data in
each AIA channel are co-aligned to remove solar rotation using the
process as described in Appendix \ref{sec:app:data}.  The result are a
set of datacubes that show the same portion of the Sun for the
duration of the data.

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{{\BF The proportion of the number of pixels in each image
    that have a given Fourier power at some sample Fourier
    frequencies.  The left hand column gives results for AIA 171\AA,
    and the right hand column, AIA 193\AA.  Regions are indicated in
    each plot title.}}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} shows the probability distribution of the
Fourier power of the pixels in each region at five selected
frequencies, for all the pixels in each region.  These distributions
are centrally peaked, show a slightly heavier tail towards lower
Fourier powers (negative skew), are slightly broader when compared to
a Gaussian distribution, and are all unimodal.  These observations
guide the choice of how to average the \PS\ over each of the selected
region.  The nature of these distributions suggest that the arithmetic
mean of the Fourier power is biased by the very largest powers.
Therefore, the mean value of the logarithm of the Fourier power is a
better description of the range of values in the data (this is
equivalent to the geometric mean of the Fourier power).  The \PA\ used
below are calculated from the mean value of the logarithm of the
Fourier power

\subsection{Results}\label{ssec:results}
Each Fourier power spectrum is fit using both models $M_{1}$ and
$M_{2}$.  The $\chi^{2}$-analog is calculated for the best fit to each
observed power spectrum.

A good fit is found if (a) the fitting routine does not report an
error, (b) the $\chi^{2}$-analog lies within the 95\% confidence
interval (see Appendix \ref{sec:app:chi}) and (c) all the parameters
found by the fitting process lie inside acceptable limits (see
Appendix \ref{sec:app:parlimits}).  This qualifies model fits as
worthy of further consideration.  The Bayesian Information Criterion
(BIC) is used to express a preference of one model over another.

The model $M_{k}$ is preferred if
\begin{equation}
BIC_{k} - BIC_{j} \le -6, \forall j\ne k.
\end{equation}

This process selects decides which model and

Figure \ref{fig:fit171193} show the fit results of each model to the
data.  For details on the fitting procedure, see Appendix
\ref{sec:app:ind}.
{\BF The two models are assessed for how well they describe the data in two
different ways. Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that Model 2 loses less information compared to Model 1,
leading to a preference for Model 2 over Model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
{\BF The AIC reveals which (out of a set of models) is preferred.  It
  does not give an assessment of the goodness-of-fit of each model.
  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
  $\chi^{2}_{r}=\sum_{j=1}^{N}\left[(P_{i}(\nu_{j})-D_{j})/\sigma_{j}^{2}\right]/(N-k-1)$,
  where $N=899$ is the number of frequencies, $P_{i}(\nu_{j})$ is the
  model power $P_{i}$ at frequency $\nu_{j}$, $D_{j}$ is the \mFpa\ at
  $\nu_{j}$, and $\sigma_{j}$ is the estimated standard deviation of
  the data $D_{j}$ (see Appendix \ref{sec:app:ind} for more details of
  the estimation of $\sigma_{j}$).  The value of $\chi^{2}_{r}$ is
  calculated for both models.  Note that the \mFpa\ are only
  approximately normally distributed, and so caution must be used in
  interpreting $\chi^{2}_{r}$. Since $N>>k$, $\chi^{2}_{r}$ is
  understood as a measure of the average scaled variance of the model
  fit to the data. Within the approximations of the analysis, the
  $\chi^{2}_{r}$ measures show that reasonable fits are obtained for
  Model $M_{2}$ in all cases, excepting the loop footpoints.  The
  relatively low value of $\chi^{2}_{r}$ for these locations indicate
  that probably the size of $\sigma_{i}$ are over-estimated.}

@@

\begin{figure}
\label{fig:spatialdistribution:preference}

\caption{Spatial distribution of model preference}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:powerlawindex}

\caption{Spatial distribution of the power law indices.  Power law
  indices are taken from either model $M_{1}$ or $M_{2}$.  Models are}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:gaussianposition}

\caption{Spatial distribution of the Gaussian position}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:gaussianwidth}

\caption{Spatial distribution of the Gaussian width}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:gaussianamplitude}

\caption{Spatial distribution of the Gaussian amplitude}
\end{figure}

\begin{figure}
\label{fig:powerlawindicescc}

\caption{Two dimensional histograms of the power law indices in every
  pair of AIA EUV channels.  The red line indicates the line where the
  power law indices are equal. Table \ref{tab:powerlawindicescc} shows
the corresponding cross correlation coefficients and the likelihood
that such a cross-correlation coefficient occurred randomly.}
\end{figure}

@@
